\thesistitle

### 2019-07-18 sections/background.tex
Uhh

>>>>

\begin{multicols}{2}
\begin{lstlisting}[caption={Functions that are type 2 clones but functionally completely different.},language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small]
// Hello.java
import javax.swing.JApplet;
import java.awt.Graphics;

public class Hello extends JApplet {
    public void paintComponent(Graphics g) {
        g.drawString("Hello, world!", 65, 95);
    }
}
\end{lstlisting}
\end{multicols}
